NLIZE: a Perturbation-Driven Visual Interrogation Tool for Analyzing and Interpreting Natural Language Inference Models

### 2018-03-25 paper/perturbation.tex
add figures

@@

\subsection{Perturbation-Driven Exploration}

Fig.~\ref{fig:modelPipeline}

Understand where and how does a model fail is the first step to improve the
model performance.
Prediction accuracy, i.e., the percentage of the correct prediction according to
the ground truth label, is the standard technique to verify the performance
of a model on a given supervised task.
%
The accuracy alone does not tell us the whole story, it provides no
information on the specific example and the condition that lead to a failure.
%
Often, the user need to examine individual failure examples to diagnostic the
issue and identify the weakness of the model.
%
However, the model may be unstable and generate the right prediction for the wrong
reason (e.g., by picking up noise in the data that is not the intended features),
therefore, we are likely to miss some important failure condition by just looking
at the failure cases.
%
An in depth analysis of the error made by the model requires the verification of
the robustness of the prediction.
%
One powerful tool to assess robustness is through the application of small
perturbation in the input and then check the variation of the prediction.
%
For example, we can replace noun and verb in the sentences with words of
similar/same meaning, such an operation is often carried out by domain experts
(subconsciously) when they try to figure out the potential issue of a model.
%
In another work, the perturbation of the input allow us to do a sensitivity
analysis on the prediction.
%
In this work, we introduce an synonyms perturbation scheme that automatically
generate the perturbation and generate the prediction and summarized the prediction
variation.
%

>>>>

\subsection{Perturbation-Driven Exploration}
To answer the questions arise during the exploration and address the analysis tasks, we adopted a .

As illustrated in Fig.~\ref{fig:modelPipeline},

@@

Often, the user need to examine individual failure examples to diagnostic the
issue and identify the weakness of the model.
%
However, the model may be unstable and generate the right prediction for the wrong
reason (e.g., by picking up noise in the data that is not the intended features),
therefore, we are likely to miss some important failure condition by just looking
at the failure cases.
%
An in depth analysis of the error made by the model requires the verification of
the robustness of the prediction.
%
One powerful tool to assess robustness is through the application of small
perturbation in the input and then check the variation of the prediction.
%
For example, we can replace noun and verb in the sentences with words of
similar/same meaning, such an operation is often carried out by domain experts
(subconsciously) when they try to figure out the potential issue of a model.
%
In another work, the perturbation of the input allow us to do a sensitivity
analysis on the prediction.
%
In this work, we introduce an synonyms perturbation scheme that automatically
generate the perturbation and generate the prediction and summarized the prediction
variation.
%

% Understand where and how does a model fail is the first step to improve the
% model performance.
% Prediction accuracy, i.e., the percentage of the correct prediction according to
% the ground truth label, is the standard technique to verify the performance
% of a model on a given supervised task.
% %
% The accuracy alone does not tell us the whole story, it provides no
% information on the specific example and the condition that lead to a failure.

### 2018-03-25 paper/predSummary.tex
add figures

@@

\subsection{Sentence View}
The sentence view shows the premise and hypothesis sentences, and in case of the existence of perturbation, highlight the where in the sentence the perturbation happens.
%
Add user customized sentences.

\begin{itemize}
\item Examine perturbed pair
\item See which word is perturbed in a sentence
\item Add to existing example collection
\end{itemize}

>>>>

\begin{figure}[htbp]
\centering
\vspace{-2mm}
 \includegraphics[width=1.0\linewidth]{summaryView}
 \caption{Explore the full development set and examine their prediction result and sensitivity.}
\label{fig:modelPipeline}
\end{figure}

@@

### 2018-03-25 paper/relatedWorks.tex
add figures

\textbf{NLP Models Visualization.}
Compare to the multitude of research for making sense of convolutional neural networks, relatively less works has been dedicated to neural linguistic models.
%
However, the previous works~\cite{KarpathyJohnson2015, LiChenHovy2015, StrobeltGehrmannPfister2018, LiuBremerJayaraman2018} not only demonstrated the benefit of visualization in understanding NLP models, but also revealed enoumous possibility for future applications.
% There is many unresolve challenge and the
The early work on charactor level recurrent network~\cite{KarpathyJohnson2015} demonstrates effectness of the hidden state in capturing the unique pattern in training text. The compositionality exibited in neural linguistic model (i.e., build sentence from meaing of words and phrases) are examined in the work by Li et al. ~\cite{LiChenHovy2015}, by utilizing methods inspired by similar work in computer vision.
The LSTMvis~\cite{StrobeltGehrmannPfister2018} work utilized a line plot style visual encoding to visualize the time varying hidden states of recurent neutural network. The word embedding visualization work~\cite{LiuBremerJayaraman2018} illustrate how semantic relationship can be recovered by linear projections in the high-dimensional word embedding space produced by word2vec~\cite{MikolovSutskeverChen2013} or glove~\cite{PenningtonSocherManning2014}.

>>>>

\textbf{NLP Models Visualization.}
Compare to the multitude of research for making sense of convolutional neural networks, relatively less works has been dedicated to neural linguistic models.
%
However, the previous works~\cite{KarpathyJohnson2015, LiChenHovy2015, StrobeltGehrmannPfister2018, LiuBremerJayaraman2018} not only demonstrated the benefit of visualization in understanding NLP models, but also revealed enoumous possibility for future applications.
% There is many unresolve challenge and the
The early work on charactor level recurrent network~\cite{KarpathyJohnson2015} demonstrates effectness of the hidden state in capturing the unique pattern in training text. The compositionality exibited in neural linguistic model (i.e., build sentence from meaing of words and phrases) are examined in the work by Li et al. ~\cite{LiChenHovy2015}, by utilizing methods inspired by similar work in computer vision.
The LSTMvis~\cite{StrobeltGehrmannPfister2018} work utilized a line plot style visual encoding to visualize the time varying hidden states of recurrent neutral network. The word embedding visualization work~\cite{LiuBremerJayaraman2018} illustrate how semantic relationship can be recovered by linear projections in the high-dimensional word embedding space produced by word2vec~\cite{MikolovSutskeverChen2013} or Glove~\cite{PenningtonSocherManning2014}.

### 2018-03-25 paper/sentence.tex
add figures

\subsection{All Pair Summary View}
\begin{itemize}
\item How go from 10k pair to one pair
\item How constitute interesting example
\item How to get a sense of overall prediction result
\end{itemize}

\subsection{Sentence View}
\begin{itemize}
\item Examine perturbed pair
\item See which word is perturbed in a sentence
\item Add to existing example collection
\end{itemize}

>>>>

\begin{figure}[htbp]
\centering
\vspace{-2mm}
 \includegraphics[width=0.85\linewidth]{sentenceView}
 \caption{Sentence view shows the premise and the hypothesis sentence pair.}
\label{fig:modelPipeline}
\end{figure}

\subsection{Sentence View}
The sentence view shows the premise and hypothesis sentences, and in case of the existence of perturbation, highlight the where in the sentence the perturbation happens.
%
Add user customized sentences.

\begin{itemize}
\item Examine perturbed pair
\item See which word is perturbed in a sentence
\item Add to existing example collection
\end{itemize}
